\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-02-02 doc/USER_MANUAL/manual_SPECFEM3D.tex
fixed minor details in the LaTeX manual

Before running the \texttt{configure} script, you should probably edit file \texttt{flags.guess} to make sure that it contains the best compiler options for your system. Known problems or things to check are:

@@

If you run very large meshes on a relatively small number
of processors, the memory size needed on each processor might become
greater than 2 gigabytes, which is the upper limit for 32-bit addressing.
In this case, on some compilers you may need to add \texttt{``-mcmodel=medium}''
to the compiler options otherwise the compiler will display an error
message (for instance \texttt{``relocation truncated to fit: R\_X86\_64\_PC32 against .bss''} or something similar);
on an IBM machine with the \texttt{xlf} and \texttt{xlc} compilers, using \texttt{-q64} is usually sufficient.

>>>>

Before running the \texttt{configure} script, you should probably edit file \texttt{flags.guess} to make sure that it contains the best compiler options for your system. Known issues or things to check are:

@@

If you run very large meshes on a relatively small number
of processors, the memory size needed on each processor might become
greater than 2 gigabytes, which is the upper limit for 32-bit addressing.
In this case, on some compilers you may need to add \texttt{``-mcmodel=medium}''
to the compiler options otherwise the compiler will display an error
message (for instance \texttt{``relocation truncated to fit: R\_X86\_64\_PC32 against .bss''} or something similar);
on an IBM machine with the \texttt{xlf} and \texttt{xlc} compilers, using \texttt{-q64} is usually sufficient.\\
